Accelerating Precision Medicine with Quantum Computing and AI\\\bigskip \LARGE\mdseries\itshape\color{black!80} Exploring the future of Personalized Health Care\par

### 2022-01-23 paper.tex
(paper) add equations

% Created 2022-01-23 Sun 13:16
% Intended LaTeX compiler: pdflatex
\documentclass{scrartcl}
\renewcommand\sectionformat{\llap{\thesection\autodot\enskip}}
\renewcommand\subsectionformat{\llap{\thesubsection\autodot\enskip}}
\renewcommand\subsubsectionformat{\llap{\thesubsubsection\autodot\enskip}}

@@

\section{Introduction}
\label{sec:org3746fb1}

@@

\section{AI in Precision Medicine}
\label{sec:orgaa38e6b}

@@

\subsection{Accelerating AI with Quantum Computing}
\label{sec:org5f9b1a5}

@@

\subsection{Hybrid Quantum-Classical Neural Networks}
\label{sec:org4513971}

@@

In this example, \(\sigma\) is a nonlinear function and \(h_{i}\) is the value of neuron i at each hidden layer. \(R(h_{i})\) represents any rotation gate about an angle equal to \(h_{i}\) and \(y\) is the final prediction value generated from the hybrid network

@@

\subsection{Generative Adversarial Networks}
\label{sec:org4a73d5d}

@@

GANs are a clever way of training a generative model by framing the problem as a supervised learning problem with two sub-models: the generator model that we train to generate new examples, and the discriminator model that tries to classify examples as either real (from the domain) or fake (generated). The two models are trained together in a zero-sum game, adversarial, until the discriminator model is fooled about half the time, meaning the generator model is generating plausible examples.

\subsubsection{MolGAN}
\label{sec:org6af9af7}

@@

\subsubsection{Qubit-efficient Quantum Molecule Generation}
\label{sec:org3384f98}

@@

\section{Prototype}
\label{sec:orgc2eb20e}

@@

\subsection{Image recognition (QuTorch-HG)}
\label{sec:orgb83bbdc}

@@

We have created a base neural network model, which utilizes hybrid machine learning to create a model trained from any dataset in ImageNet format. The base model is used as the base for Transfer Learning, on an Image Classification task (based on resnet18). The last layer of this pre-trained model (fully-connected/fc layer) is then modified through a quantum machine learning framework, generating a new model. We will be testing its efficiency, practicality, and accuracy. We are training the model with 4 Qubits at 8 epochs.

\subsection{Quantum Accelerated Drug \& Molecule Generation (QGAN-HG)}
\label{sec:org76ff07f}

@@

\subsection{Data}
\label{sec:org25dde5d}

@@

\subsection{Tools and Hardware}
\label{sec:orgdbffe93}

@@

\section{Results}
\label{sec:orga8ccec7}

\subsection{Speed}
\label{sec:orgfc5ab1f}

@@

\subsection{Accuracy}
\label{sec:org8b71621}

@@

\subsection{Pricing}
\label{sec:org2502bef}

@@

\section{Conclusion and Further Research}
\label{sec:org1f114d9}

\section{References}
\label{sec:orgddb3177}

>>>>

% Created 2022-01-23 Sun 14:08
% Intended LaTeX compiler: pdflatex
\documentclass{scrartcl}
\renewcommand\sectionformat{\llap{\thesection\autodot\enskip}}
\renewcommand\subsectionformat{\llap{\thesubsection\autodot\enskip}}
\renewcommand\subsubsectionformat{\llap{\thesubsubsection\autodot\enskip}}

@@

\section{Introduction}
\label{sec:org48ebeae}

@@

\section{AI in Precision Medicine}
\label{sec:org3e99254}

@@

\subsection{Accelerating AI with Quantum Computing}
\label{sec:org9e9021c}

@@

\subsection{Hybrid Quantum-Classical Neural Networks}
\label{sec:org00af154}

@@

Each classical equation is modeled through the nonlinear function

\begin{align}
h_{x}=\sigma(w_{a}x_{a}+w_{b}x_{b}+w_{c}x_{c})
\end{align}

where \(h_{i}\) is the value of neuron i at each hidden layer. \(R(h_{i})\) represents any rotation gate about an angle equal to \(h_{i}\) and \(y\) is the final prediction value generated from the hybrid network.

@@

\subsection{Generative Adversarial Networks}
\label{sec:org29e917a}

@@

GANs are a clever way of training a generative model by framing the problem as a supervised learning problem with two sub-models: the generator model that we train to generate new examples, and the discriminator model that tries to classify examples as either real (from the domain) or fake (generated). The two models are trained together in a zero-sum game, adversarial, until the discriminator model is fooled about half the time, meaning the generator model is generating plausible examples. This can be modeled through the equation

\begin{align}
\min_{G}\max_{D}\mathbb{E}_{x\sim p_{\text{data}}(x)}[\log{D(x)}] +  \mathbb{E}_{z\sim p_{\text{generated}}(z)}[1 - \log{D(G(z))}]
\end{align}

\subsubsection{MolGAN}
\label{sec:org07a4bd5}

@@

\subsubsection{Qubit-efficient Quantum Molecule Generation}
\label{sec:org7497f82}

@@

\section{Prototype}
\label{sec:orgc004852}

@@

\subsection{Image recognition (QuTorch-HG)}
\label{sec:orgb3d0933}

@@

We have created a base neural network model, which utilizes hybrid machine learning to create a model trained from any dataset in ImageNet format. The base model is used as the base for Transfer Learning, on an Image Classification task (based on resnet18). The last layer of this pre-trained model (fully-connected/fc layer) is then modified through a quantum machine learning framework, generating a new model. We will be testing its efficiency, practicality, and accuracy. We are training the model with 4 Qubits at 8 epochs. Loss is calculated using the Huber loss method, with the following equation

\begin{align}
L_{\delta}=
    \left\{\begin{matrix}
        \frac{1}{2}(y - \hat{y})^{2} & if \left | (y - \hat{y})  \right | < \delta\\
        \delta ((y - \hat{y}) - \frac1 2 \delta) & otherwise
    \end{matrix}\right.
\end{align}

Accuracy is calculated via a confusion matrix, with the following metrics

\begin{align}
Accuracy &= \frac{TP+TN}{TP+TN+FP+FN}\\
Precision &= \frac{TP}{TP+FP}\\
Recall &= \frac{TP}{TP+FN}\\
F1 &= \frac{2*Precision*Recall}{Precision+Recall} = \frac{2*TP}{2*TP+FP+FN}
\end{align}

\subsection{Quantum Accelerated Drug \& Molecule Generation (QGAN-HG)}
\label{sec:org00e2ec5}

@@

\subsection{Data}
\label{sec:org269d80a}

@@

\subsection{Tools and Hardware}
\label{sec:org2908f15}

@@

\section{Results}
\label{sec:orgde3234d}

\subsection{Speed}
\label{sec:orgc8c028e}

@@

\subsection{Accuracy}
\label{sec:org18efb0c}

@@

\subsection{Pricing}
\label{sec:org101ffef}

@@

\section{Conclusion and Further Research}
\label{sec:orgba86c27}

\section{References}
\label{sec:orgc0f0fd3}
